\vspace{-2cm}A generative model for urban firm networks

### 2020-09-11 main.tex
Update on Overleaf.

We finally design scenarios to evaluate the impact of economic shocks. These can be the consequence of diverse factors, including socio-economic, geopolitical factors (example of Brexit), or other unpredicted human disasters such as the COVID-19 pandemic. We simulate border closures by rescaling $c_0$ -- the range parameter for socio-economic interactions --, and intra-country lock-downs by rescaling $d_0$ -- the range parameter for direct interactions -- during the simulation, with other parameters being fixed to their default values and the model setup in the real configuration. More precisely, with $t_f = 5000$, the model is run for $t_f / 2$ steps. Then, following two new rate parameters $\kappa_C \in \left[0;1\right]$ and $\kappa_G \in \left[0;1\right]$ defining the shock, model parameters are updated as $\kappa_G \cdot d_0$ and $\kappa_C \cdot c_0$. The model is then run for the remaining time steps until $t_f$. We study the temporal trajectory of indicators to see the impact of the shock in time. The experiment is run for $(\kappa_G,\kappa_C)$ ranging between 0.2 (strong restrictions) to 1 (reference trajectory), with 100 model repetitions.

>>>>

We finally design scenarios to evaluate the impact of economic shocks. These can be the consequence of diverse factors, including socio-economic, geopolitical factors (example of Brexit), or other unpredicted human disasters such as the COVID-19 pandemic. We simulate border closures by rescaling $c_0$ -- the range parameter for socio-economic interactions --, and intra-country lock-downs by rescaling $d_0$ -- the range parameter for direct interactions -- during the simulation, with other parameters being fixed to their default values and the model setup in the real configuration. More precisely, with $t_f = 5000$, the model is run for $t_f / 2$ steps. Then, following two new rate parameters $\kappa_C \in \left[0;1\right]$ and $\kappa_G \in \left[0;1\right]$ defining the shock, model parameters are updated as $d_0 = \kappa_G \cdot d_0$ and $c_0 = \kappa_C \cdot c_0$. The model is then run for the remaining time steps until $t_f$. We study the temporal trajectory of indicators to see the impact of the shock in time. The experiment is run for $(\kappa_G,\kappa_C)$ ranging between 0.2 (strong restrictions) to 1 (reference trajectory), with 100 model repetitions.
